BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-15 tex/1-intro.tex
Update 1-intro.tex

Blogs disappear every day. Losing data is obviously undesirable, but even more so when this data has historic, politic or scientific value. In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation. Yet, blogs are an important part of today's web: the WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}. Blogs also showed to be an important resources during the 2011 Egyptian revolution where they played an instrumental role in the organization and implementation of protests. \cite{nahedeltantawy2012}\comment{not sure where to put this one}. The need for preservation for this volatile communication medium is today a necessity.\comment{Do you have a better closing sentence?}

Among the challenges in developing a blog archiving software is providing an automatic web crawler to traverse blogs and accurately their content. The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary. The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited by the ever-changing structure of blog contents. Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, invalidating traditional web crawling techniques.

@@

\begin{itemize}
  \item We present a new generic algorithm to build extraction from a set of pages and target content. We then derive an optimized reformulation tied to a particular string similarity and show that this reformulated algorithm has a linear time complexity.
  \item We show how to use this algorithm to extract blog articles, and how it can be adapted to extract authors, publication dates and comments.
  \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
  \item We show who use make use of a complete web browser to render JavaScript powered web pages before processing them. This step allows our crawler to effectively harvest blogs build with modern technology, such at the increasingly popular third-party commenting systems.
  \item We present and analyze performance results of our algorithm in terms of extraction success rates and execution time. A comparison is made with three state-of-the-art article extraction algorithms.
\end{itemize}

>>>>

Blogs disappear every day. Losing data is obviously undesirable, but even more so when this data has historic, politic or scientific value. In contrast to books, newspapers or centralized web platforms like Facebook, there is no standard method or authority to ensure blog archiving and long-term digital preservation. Yet, blogs are an important part of today's web: the WordPress reports more than 33 million new posts and 48 million new comments each month \cite{wordpress2014}. Blogs also showed to be an important resource during the 2011 Egyptian revolution by playing an instrumental role in the organization and implementation of protests. \cite{nahedeltantawy2012}\comment{not sure where to put this one}. The need for preservation for this volatile communication medium is today a necessity.\comment{Do you have a better closing sentence?}

Among the challenges in developing a blog archiving software is* providing an automatic web crawler to \TODO{better keyword} traverse blogs and accurately extract their content. The sheer size of the blogosphere combined with an unpredictable publishing rate of new information call for a highly scalable system, while the lack of programmatic access to the complete blog content makes the use of automatic extraction techniques necessary. The variety of available blog publishing platforms offers a limited common set of properties that a crawler can exploit, further limited by the ever-changing structure of blog contents. Finally, an increasing number of blogs heavily rely on dynamically created content to present information, using the latest web technologies, hence invalidating traditional web crawling techniques.

@@

\begin{itemize}
  \item We present a new generic algorithm to build extraction from a set of pages and target content. We then derive an optimized reformulation tied to a particular string similarity and show that this reformulated algorithm has a linear time complexity.
  \item We show how to use this algorithm to extract blog articles, and how it can be adapted to extract authors, publication dates and comments.
  \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
  \item We show how we make use of a complete web browser to render JavaScript powered web pages before processing them. This step allows our crawler to effectively harvest blogs built with modern technology, such as the increasingly popular third-party commenting systems.
  \item We present and analyze performance results of our algorithm in terms of extraction success rates and execution time. A comparison is made with three state-of-the-art article extraction algorithms.
\end{itemize}
